A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-20 manuscript.Rmd
minor edits

From the `Dockerfile` you can then build an image.
While you can do so manually we prefer to use Make, see [Internal Dependencies].
The `Makefile` build by `repro` does contain a recipe for creating the `Dockerfile`.

@@

The `Makefile` from `repro` does also include a mechanism to send commands conditionally through the Docker container.
This mechanism is triggered by `DOCKER=TRUE` in the make call:

```bash
# this should be run in the terminal
make DOCKER=TRUE
```
The function `automate()` combines `automate_docker()` & `automate_make()`.

You can also manually edit the `Dockerfile` by amending the file `.repro/Dockerfile_manual` to install software beyond R packages.
Remember to run `repro::automate()` after you made edits to `.repro/Dockerfile_manual`.
We recommend @wiebelsLeveragingContainersReproducible2021 as a starting point for researcher who want to better understand how they can employ Docker for research.

>>>>

From the `Dockerfile` you can then build an image.
While you can do so manually, we suggest to again use Make ( see [Internal Dependencies]).
The `Makefile` built by `repro` does contain a recipe for creating the `Dockerfile`.

@@

Importantly, the `Makefile` created by `repro` includes a mechanism to execute commands in the Docker container instead of locally.
This mechanism is triggered by the argument `DOCKER=TRUE` appended to any make call. 
The following call builds all targets inside the container instead of in the local computing environment:

```bash
# this should be run in the terminal
make DOCKER=TRUE
```

Last, to create or update the container and all Make targets, `repro` provides a single function `automate()` that calls `automate_docker()` and `automate_make()`.

You can also manually edit the `Dockerfile` by changing the file `.repro/Dockerfile_manual` to install software other than R packages.
Remember to run `repro::automate()` every time you made edits to `.repro/Dockerfile_manual`.
We recommend @wiebelsLeveragingContainersReproducible2021 as a starting point for researcher who want to better understand how they can employ Docker for research.
